Avoiding tipping points in the management of ecological systems: a non-parametric Bayesian approach

### 2013-06-17 inst/doc/beyond-mechanistic-models.Rmd
code examples updated

<!-- Run R code for analysis, to be called by figures -->
```{r, echo=FALSE, cache=FALSE, include=FALSE}
options(xtable.print.comment=FALSE)
options(xtable.type = 'latex', table.placement="H")
opts_chunk$set(warning=FALSE, message=FALSE, comment=NA,
               tidy=FALSE, echo=FALSE)
opts_knit$set(progress = TRUE, verbose = TRUE)
opts_chunk$set(dev = 'Cairo_pdf', fig.width=5.5, fig.height=4,
 cache.path = 'cache-pdf/', cache=TRUE, external=TRUE)
read_chunk("nonparametric-bayes.R")
```
```{r knit-settings, echo=FALSE, include=FALSE, cache=FALSE}
```
```{r libraries, echo=FALSE, include=FALSE}
```
```{r plotting-options, echo=FALSE, include=FALSE}
```
```{r stateeq}
```
```{r sdp-pars, dependson="stateeq"}
```
```{r obs, dependson="sdp-pars"}
```
```{r mle, dependson="obs"}
```
```{r gp-priors}
```
```{r gp, dependson=c("obs", "gp-priors")}
```
```{r opt, dependson=c("gp", "mle")}
```
```{r sim, dependson="opt"}
```

@@

```{r gp_plot, dependson=c("gp", "mle", "plotting-options"), fig.cap="Graph of the inferred Gaussian process compared to the true process and maximum-likelihood estimated process.  Graph shows the expected value for the function $f$ under each model.  Two standard deviations from the estimated Gaussian process covariance with (light grey) and without (darker grey) measurement error are also shown.  The training data is also shown as black points.  (The GP is conditioned on 0,0, shown as a pseudo-data point). "}
```

```{r policies_plot, dependson=c("opt", "plotting-options"), fig.cap="The steady-state optimal policy (infinite boundary) calculated under each model.  Policies are shown in terms of target escapement, $S_t$, as under models such as this a constant escapement policy is expected to be optimal [@Reed1979]."}
```

```{r sim_plot, dependson=c("sim", "plotting-options"), fig.cap="Gaussian process inference outperforms parametric estimates. Shown are 100 replicate simulations of the stock dynamics (eq 1) under the policies derived from each of the estimated models, as well as the policy based on the exact underlying model."}
```

>>>>

<!-- Run R code for analysis, to be called by figures -->
```{r generics-and-libraries, cache=FALSE, message=FALSE, warning=FALSE, include=FALSE}
source("~/.knitr_defaults.R")
library(knitcitations)
library(nonparametricbayes) 
opts_chunk$set(external=TRUE)
read_chunk("../examples/BUGS/external-chunks.R")
```

```{r plotting-options, echo=FALSE, cache=FALSE, include=FALSE}
options(xtable.print.comment=FALSE)
options(xtable.type = 'latex', table.placement="H")
opts_chunk$set(warning=FALSE, message=FALSE, comment=NA,
               tidy=FALSE, echo=FALSE)
opts_knit$set(progress = TRUE, verbose = TRUE)
opts_chunk$set(dev = 'Cairo_pdf', fig.width=5.5, fig.height=4,
 cache.path = 'cache-pdf/', cache=TRUE, external=TRUE)
```

```{r posterior-mode}
```
```{r stateeq}
```
```{r sdp-pars, dependson="stateeq"}
```
```{r obs, dependson="sdp-pars"}
```

```{r mle, dependson="obs"}
```
```{r mle-output, dependson="mle"}
```

```{r gp-priors}
```
```{r gp, dependson=c("gp-priors", "obs")}
```
```{r gp_traces_densities, dependson="gp"}
```
```{r gp-output, dependson="gp"}
```

```{r jags-setup}
```
```{r common-priors}
```
```{r allen-model}
```
```{r allen-priors, dependson="common-priors"}
```
```{r allen-mcmc, dependson=c("allen-model", "allen-pars", "jags-setup"), results="hide"}
```
```{r allen-traces, dependson="allen-mcmc"}
```
```{r allen-posteriors, dependson=c("allen-traces", "allen-priors")}
```
```{r allen-output, dependson=c("posterior-mode", "allen-traces")}
```

```{r ricker-model}
```
```{r ricker-priors, dependson="common-priors"}
```
```{r ricker-mcmc, dependson="ricker-model"}
```
```{r ricker-traces, dependson="ricker-mcmc"}
```
```{r ricker-posteriors, dependson=c("ricker-traces", "ricker-priors")}
```
```{r ricker-output, dependson=c("posterior-mode", "ricker-traces")}
```

```{r myers-model}
```
```{r myers-priors}
```
```{r myers-mcmc, dependson="myers-model"}
```
```{r myers-traces, dependson="myers-mcmc"}
```
```{r myers-posteriors, dependson="myers-traces"}
```
```{r myers-output, dependson=c("posterior-mode", "myers-traces")}
```

```{r assemble-models, dependson=c("myers-output", "ricker-output", "allen-output", "gp-output", "mle-output")}
```
``{r gp-opt, dependson="gp-output"}
```
```{r mle-opt, dependson="mle-output"}
```
```{r allen-opt, dependson="allen-output"}
```
```{r ricker-opt, dependson="ricker-output"}
```
```{r myers-opt, dependson="myers-output"}
```
```{r assemble-opt, dependson=c("gp-opt", "mle-opt", "allen-opt", "ricker-opt", "myers-opt")}
```
```{r sims, dependson="assemble-opt"}
```

```{r profits, dependson="sims", results="hide"}
```
```{r deviances, dependson=c("posterior-mode", "myers-output", "ricker-output", "allen-output", "gp-output", "mle-output"), results="hide"}
```

@@

```{r Figure1, dependson=c("assemble-models"), fig.cap="Graph of the inferred Gaussian process compared to the true process and maximum-likelihood estimated process.  Graph shows the expected value for the function $f$ under each model.  Two standard deviations from the estimated Gaussian process covariance with (light grey) and without (darker grey) measurement error are also shown.  The training data is also shown as black points.  (The GP is conditioned on 0,0, shown as a pseudo-data point). "}
```
```{r Figureb, dependson=c("assemble-models", "par-fns")}
```

```{r Figure2, dependson="assemble-opt", fig.cap="The steady-state optimal policy (infinite boundary) calculated under each model.  Policies are shown in terms of target escapement, $S_t$, as under models such as this a constant escapement policy is expected to be optimal [@Reed1979]."}
```

```{r Figure3, dependson=c("sim", "plotting-options"), fig.cap="Gaussian process inference outperforms parametric estimates. Shown are 100 replicate simulations of the stock dynamics (eq 1) under the policies derived from each of the estimated models, as well as the policy based on the exact underlying model."}
```

```{r Figure4, dependson="profits"}
```

### 2013-06-17 inst/doc/nonparametric-bayes.Rmd
code examples updated

<!-- Run R code for analysis, to be called by figures -->
```{r generics-and-libraries, cache=FALSE, message=FALSE, warning=FALSE, include=FALSE}
source("~/.knitr_defaults.R")
library(knitcitations)
library(nonparametricbayes) 
opts_chunk$set(external=TRUE)
read_chunk("../examples/BUGS/external-chunks.R")
```

```{r plotting-options, echo=FALSE, cache=FALSE, include=FALSE}
options(xtable.print.comment=FALSE)
options(xtable.type = 'latex', table.placement="H")
opts_chunk$set(warning=FALSE, message=FALSE, comment=NA,
               tidy=FALSE, echo=FALSE)
opts_knit$set(progress = TRUE, verbose = TRUE)
opts_chunk$set(dev = 'Cairo_pdf', fig.width=5.5, fig.height=4,
 cache.path = 'cache-pdf/', cache=TRUE, external=TRUE)
```

@@

```{r Figure3, dependson=c("sim", "plotting-options"), fig.cap="Gaussian process inference outperforms parametric estimates. Shown are 100 replicate simulations of the stock dynamics (eq 1) under the policies derived from each of the estimated models, as well as the policy based on the exact underlying model."}
```

@@

```{r Figure4, dependson="profits", fig.cap="Histograms of the realized net present value of the fishery over a range of simulated data and resulting parameter estimates. For each data set, the three models are estimated as described above. Values plotted are the averages of a given policy over 100 replicate simulations. Details and code provided in the supplement."}
```

>>>>

<!-- Run R code for analysis, to be called by figures -->
```{r generics-and-libraries, cache=FALSE, message=FALSE, warning=FALSE, include=FALSE}
library(nonparametricbayes) 
opts_chunk$set(external=TRUE)
read_chunk("../examples/BUGS/external-chunks.R")
```

```{r pdf-options, echo=FALSE, cache=FALSE, include=FALSE}
library(ggplot2)
options(xtable.print.comment=FALSE)
options(xtable.type = 'latex', table.placement="H")
opts_knit$set(progress = TRUE, verbose = TRUE)
opts_chunk$set(dev = 'Cairo_pdf', fig.width=5.5, fig.height=4,
 cache.path = 'cache-pdf/', cache=TRUE, external=TRUE)
opts_chunk$set(warning=FALSE, message=FALSE, comment=NA,
               tidy=FALSE, echo=FALSE)
```

@@

```{r Figure3, dependson=c("sim", "pdf-options"), fig.cap="Gaussian process inference outperforms parametric estimates. Shown are 100 replicate simulations of the stock dynamics (eq 1) under the policies derived from each of the estimated models, as well as the policy based on the exact underlying model."}
```

@@

```{r Figure4, dependson=c("profits", "pdf-options"), fig.cap="Histograms of the realized net present value of the fishery over a range of simulated data and resulting parameter estimates. For each data set, the three models are estimated as described above. Values plotted are the averages of a given policy over 100 replicate simulations. Details and code provided in the supplement."}
```
